Download data

### 2024-05-08 scripts/subsetDataforCrews.Rmd
fn to write out 3 sdm data products by species

ptest <- mask(ptest, blm_surf_sub)
trim(ptest)
plot(ptest)

a <- lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, 
            seed_zones = seed_zones, pSTZs = ptest) # 24 pts, 245 polys

@@

```{r}
f <- system.file("ex/elev.tif", package="terra")
r <- rast(f)
msk <- ifel(r < 400, NA, 1)

m <- mask(r, msk)

f <- system.file("ex/lux.shp", package="terra")
v <- vect(f)[1,]

mv1 <- mask(r, v)
plot(mv1)
```

>>>>

ptest <- mask(ptest, blm_surf_sub)
ptest <- trim(ptest)
plot(ptest)

crew_dir <-  '/media/steppe/hdd/2024SOS_CrewGeospatial/Uncompahgre - P102085'
lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, 
            seed_zones = seed_zones, pSTZs = ptest) # 24 pts, 245 polys

@@
